---
title: "Japan Census Shapefiles"
output: html_vignette
bibliography: jpucdbib.bib
vignette: >
  %\VignetteIndexEntry{Japan Census Shapefiles}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(jpucd)
```
This package includes shapefiles for local census districts in Ibaraki Prefecture covering 
    the six censuses. These as well as shapefiles for all prefectures can also be downloaded from 
    [e-Stat](https://www.e-stat.go.jp/gis/statmap-search?page=1&type=2&aggregateUnitForBoundary=A&toukeiCode=00200521).

# Original files

The original shapefiles are in kmz format wrapped in a zip file. The first task is to extract and 
    convert these to geojson. A kmz file is a zipped kml file so the first step is to unzip twice.

Copies of the original files for Ibaraki Prefecture are in extdata.
```{r}
list.files(system.file("extdata",package="jpucd"))
```
openkmzzip places the contained kml file in the R temp file folder and returns its path.

```{r}
library(jpucd)
library(zip)
shppath <- system.file("extdata",package="jpucd")
shpfile <- paste(shppath,list.files(shppath,pattern=".zip")[1],sep="/")
kmlfile <- openkmzzip(shpfile)
```

These Japanese census shapefiles conform to [KML 2.2](http://www.opengis.net/kml/2.2). Each Placemark element 
    contains ExtendedData that is particularly useful for identifying placemarks and can be used 
    for developing mappings from postal addresses to census districts.

|Field|Typical value|Description|
|:---------|:-------------|:------------|
|KEY_CODE|082010010|Census district id code, 9 or 11 digits|
|PREF|08|Prefecture
|CITY|201|Municipality. May be city, ward (in Tokyo), village, etc
|S_AREA|001000|Subarea - first 4 digits at cho-oaza level, last 2 at chome-aza level
|PREF_NAME|茨城県|Name of prefecture in Japanese
|CITY_NAME|水戸市|Name of municipality
|S_NAME|青柳町|Name of subarea
|KIGO_E||
|HCODE|8101|
|AREA|2327255.25|Area district in square meters
|PERIMETER|9591.49414|Perimeter of area
|h12kaxx_|803|
|h12kaxx_ID|802|
|KEN|08|Number of prefecture
|KEN_NAME|茨城県|Name of prefecture
|SITYO_NAME||
|DUMMY1||
|GST_NAME|水戸市|
|CSS_NAME||
|KIHON1|0010|Cho-aza level code
|DUMMY2|-|
|KIHON2|00|Chome-aza level code
|KEYCODE1|201001000|
|DUMMY3||
|KEYCODE2|2010010|
|AREA_MAX_F|M|
|KIGO_D||
|N_KEN||
|N_CITY||
|N_C1|0|
|KIGO_I||
|TATE|0|
|DIR|0|
|HIGHT|50|Height in meters
|JIKAKU|10|
|NMOJI|3|Number of characters in MOJI
|DUMMY4||
|MOJI|青柳町|Name of subarea
|SEQ_NO2|802|
|KSUM|20|
|CSUM|22|
|JINKO|2366|Population
|SETAI|877|Number of households
|X_CODE|140.480499|
|Y_CODE|36.392635|
|KCODE1|0010-00|
-----------------------------------------

Notes:
(@) KEY_CODE 
KEY_CODE is a unique id for the census district and can be used to 
    relate geojson shapes to district data extracted to a separate 
    csv file. To make into a usable id, 9-digit codes needed to be 
    zero-padded to 11 digits. The full 11-digit code is a concatenation 
    of PREF, CITY, KIHON1 and KIHON2 codes.
(@) S_NAME
S_NAME is usually the geographic name of the district but has issues.
    This field is not standardized across prefectures and is 
    particularly problematic in Kyoto Prefecture. Named districts may 
    contain other named districts whose names are not in this 
    extended data. These names apparently derive from folder names used
    by local census offices to manage census tasks.

 
