---
title: "Japan Census Shapefiles"
output: html_vignette
bibliography: jpucdbib.bib
vignette: >
  %\VignetteIndexEntry{Japan Census Shapefiles}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(jpucd)
```
This package includes shapefiles for local census districts in Ibaraki Prefecture covering 
    the six censuses. These as well as shapefiles for all prefectures can also be downloaded from 
    [e-Stat](https://www.e-stat.go.jp/gis/statmap-search?page=1&type=2&aggregateUnitForBoundary=A&toukeiCode=00200521).

# Original files

The original shapefiles are in kmz format wrapped in a zip file. The first task is to extract and 
    convert these to geojson. A kmz file is a zipped kml file so the first step is to unzip twice.

Copies of the original files for Ibaraki Prefecture are in extdata.
```{r}
list.files(system.file("extdata",package="jpucd"))
```
openkmzzip places the contained kml file in the R temp file folder and returns its path.

```{r}
library(jpucd)
library(zip)
shppath <- system.file("extdata",package="jpucd")
shpfile <- paste(shppath,list.files(shppath,pattern=".zip")[1],sep="/")
kmlfile <- openkmzzip(shpfile)
```

Currently, the external data contains the following files:

|File name|Format|Census type|Census year|Prefecture|Notes|
|:-----------|:----------|:--------:|:--------:|:--------|:---------------|
|A002005212000DDKWC08.zip|Zipped kml|General|2000|Ibaraki|Original file from eStat|
|A002005522009DDKWC08.zip|Zipped kml|Economic|2009|Ibaraki|Original file from eStat|
|A002005522014DDKWC08.zip|Zipped kml|Economic|2014|Ibaraki|Original file from eStat|
|JPgenlCY2000P08Ibaraki.geojson.zip|Zipped geojson|General|2000|Ibaraki|Converted from eStat file|
|JPgenlCY2005P08Ibaraki.geojson.zip|Zipped geojson|General|2005|Ibaraki|Converted from eStat file|
|JPgenlCY2010P08Ibaraki.geojson.zip|Zipped geojson|General|2010|Ibaraki|Converted from eStat file|
|JPgenlCY2015P08Ibaraki.geojson.zip|Zipped geojson|General|2000|Ibaraki|Converted from eStat file|


# Extended data - Original general census files from eStat

These Japanese census shapefiles conform to [KML 2.2](http://www.opengis.net/kml/2.2). Each Placemark element 
    contains ExtendedData that is particularly useful for identifying placemarks and can be used 
    for developing mappings from postal addresses to census districts.

|Field|Typical value|Description|
|:---------|:-------------|:------------|
|KEY_CODE|082010010|Census district id code, 9 or 11 digits|
|PREF|08|Prefecture
|CITY|201|Municipality. May be city, ward (in Tokyo), village, etc
|S_AREA|001000|Subarea - first 4 digits at cho-oaza level, last 2 at chome-aza level
|PREF_NAME|茨城県|Name of prefecture in Japanese
|CITY_NAME|水戸市|Name of municipality
|S_NAME|青柳町|Name of subarea
|KIGO_E|E1|Flag for districts that have multiple shapes. (See note below.)  
|HCODE|8101|
|AREA|2327255.25|Area district in square meters
|PERIMETER|9591.49414|Perimeter of area
|h12kaxx_|803|
|h12kaxx_ID|802|
|KEN|08|Number of prefecture
|KEN_NAME|茨城県|Name of prefecture
|SITYO_NAME||
|DUMMY1||
|GST_NAME|水戸市|
|CSS_NAME||
|KIHON1|0010|Cho-aza level code
|DUMMY2|-|
|KIHON2|00|Chome-aza level code
|KEYCODE1|201001000|
|DUMMY3||
|KEYCODE2|2010010|
|AREA_MAX_F|M|
|KIGO_D||
|N_KEN||
|N_CITY||
|N_C1|0|
|KIGO_I||
|TATE|0|
|DIR|0|
|HIGHT|50|Height in meters
|JIKAKU|10|
|NMOJI|3|Number of characters in MOJI
|DUMMY4||
|MOJI|青柳町|Name of subarea
|SEQ_NO2|802|
|KSUM|20|
|CSUM|22|
|JINKO|2366|Population
|SETAI|877|Number of households
|X_CODE|140.480499|
|Y_CODE|36.392635|
|KCODE1|0010-00|
-----------------------------------------

Notes:

(@) KEY_CODE 

KEY_CODE is a unique id for the census district and can be used to 
    relate geojson shapes to district data extracted to a separate 
    csv file. To make into a usable id, 9-digit codes needed to be 
    zero-padded to 11 digits. The full 11-digit code is a concatenation 
    of PREF, CITY, KIHON1 and KIHON2 codes. The KEY_CODE field in eStat 
    shapefiles has severe quality control issues. In this project, 
    unique ids are created by concatenating the digit "1", PREF, CITY, 
    KIHON1 and KIHON2 fields. The digit "1" serves as a version code; 
    unified districts replace this with the digit "2".

(@) S_NAME

S_NAME is usually the geographic name of the district but has issues.
    This field is not standardized across prefectures and is 
    particularly problematic in Kyoto Prefecture. Named districts may 
    contain other named districts whose names are not in this 
    extended data. These names apparently derive from folder names used
    by local census offices to manage census tasks.

(@) KIGO_E

KIGO_E flags districts with multiple shapes. Shapes are labeled E1, E2, etc. 
    District stats such as population are gathered under shape E1.

# Extended data - Original economic census files from eStat

Shapefiles for the economic census generally correspond to those of the general census.
    However, enumeration at the cho-oaza and chome-koaza levels differs. If there are 
    no chome-koaza sublevels, the final 6 digits of S_AREA and AZA_CODE are idential
    to the first 6 digits. If there are sublevels, the first 6 digits indicate the 
    cho-oaza level and the last 6 digits designate the sublevel. For the first sublevel
    of the set, the last and first 6 digits are identical. 

|Field|Typical value|Description|
|:---------|:-------------|:------------|
|KEY_CODE|082010000000018|Census district id code, 15 digits|
|PREF|08|Prefecture
|CITY|201|Municipality. May be city, ward (in Tokyo), village, etc
|S_AREA|001600001800|Subarea - first 6 digits at cho-oaza level, last 6 at chome-aza level
|PREF_NAME|茨城県|Name of prefecture in Japanese
|CITY_NAME|水戸市|Name of municipality
|S_NAME|泉町３丁目|Name of subarea
|KIGO_E||Flag for districts that have multiple shapes. (See note below.)  
|AREA|62497.287|Area district in square meters
|PERIMETER|1029.752|Perimeter of area in meters
|KEN|08|Number of prefecture
|KEN_NAME|茨城県|Name of prefecture
|CSS_NAME|水戸市|
|MOJI|泉町３丁目|Name of subarea
|AZA_CODE|001600001800|Cho-aza level code
|AREA_MAX_F|M|
|KIGO_D||
|N_KEN||
|N_CITY||
|N_C1|0|
|KIGO_I||
|JIGYOSHO|180|
|JUGYOSHA|2109|
|X_CODE|140.46115|
|Y_CODE|36.37999|
|KEYCODE1|2010000000018|
-----------------------------------------

Notes:

(@) KEY_CODE 

KEY_CODE is an id for the census district and can be used to 
    relate geojson shapes to district data extracted to a separate 
    csv file. It may not be unique but can be made unique in combination
    with KIGO_E.

(@) S_NAME

(@) KIGO_E

KIGO_E flags districts with multiple shapes. Shapes are labeled E1, E2, etc. 
    District stats such as population are gathered under shape E1.

